Confirmation of Wide-Field Signatures in Redshifted 21~cm Power Spectra using Murchison Widefield Array Observations

### 2015-04-09 ms.tex
Minor change in Summary
From e188012:
============

In ms.tex,

(*) Minor change in Summary

For future work, we plan to extend our analysis to the upcoming instrument, HERA, which is currently under construction. It is a closely packed hexagonal array of fixed 14~m dishes which will observe the sky drifting overhead with redundant antenna spacings. Based on our earlier study, such a dish will have a much desirable Fourier response from a foreground contamination viewpoint. One of our objectives is to forecast the per-baseline foreground contamination as a function of local sidereal time in order to tune the observing strategy and data analysis to maximize sensitivity to the EoR signal.

>>>>

For future work, we plan to extend our analysis to the upcoming instrument, HERA, which is currently under construction. It is a closely packed hexagonal array of fixed 14~m dishes which will observe the sky drifting overhead with redundant antenna spacings. Based on our earlier study, such a dish will have a much desirable Fourier response from a foreground contamination viewpoint. One of our objectives is to forecast the per-baseline foreground contamination as a function of local sidereal time in order to tune the HERA observing strategy and data analysis to maximize sensitivity to the EoR signal.
